Nonlinear Models
=================
Explore the use of nonlinear models using some tools in R.

```{r}
require(ISLR)
attach(Wage)
```

Polynomials
-------------
First we will use polynomials and focus on a single predictor age: (They are orthogonal polynomials)
```{r}
fit = lm(wage~poly(age,4), data=Wage)
summary(fit)
```

Lets make a plot of the fitted function, along with the standard errors of the fit.
```{r fig.width=7, fig.height=6}
agelims = range(age)
age.grid = seq(from=agelims[1], to=agelims[2])
preds = predict(fit, newdata=list(age=age.grid),se=TRUE)
se.bands = cbind(preds$fit+2*preds$se, preds$fit-2*preds$se)
plot(age,wage,col='darkgrey')
lines(age.grid, preds$fit, lwd=2,col='blue')
matlines(age.grid,se.bands,col='blue',lty=2)
```

There are other more direct ways of doing this in R. For example,
```{r}
fita = lm(wage~age+I(age^2)+I(age^3)+I(age^4),data=Wage)
summary(fita)
```

The coefficients are different to those we got before! However the fits are the same:
```{r}
plot(fitted(fit),fitted(fita))
```

